PLANETESIMAL ACCRETION AT SHORT ORBITAL PERIODS

### 2022-01-12 main.tex
Add figure showing smooth accretion history, add discussion of figure 9

Next, we compare the effect of varying the initial solid surface density profile on the resulting planetesimal and embryo distribution. The final orbital period-eccentricity state of the particles is shown in figure \ref{fig:surfden_profiles}, with point sizes indicating the relative masses of the bodies. There is a clear trend between solid surface density at a given orbital period and the eccentricities of the remaining planetesimals. This trend is largely set by the initial conditions, as the gravitational stirring is more vigorous when bodies are packed together closely and higher eccentricities are required to produce an equilibrating aerodynamic drag force (see equations \ref{eq:eq:vs_timescale} and \ref{eq:ts_stokes}). Despite having significantly different masses, the planetary embryos formed in each case have remarkably similar eccentricities. This is likely due to the fact that inelastic collisions play a more significant role where the solid surface density is highest, which offsets the fact that the initial bodies started off in a dynamically hotter state.

@@

>>>>

Next, we compare the effect of varying the initial solid surface density profile on the resulting planetesimal and embryo distribution. The final orbital period-eccentricity state of the particles is shown in figure \ref{fig:surfden_profiles}, with point sizes indicating the relative masses of the bodies. There is a clear trend between solid surface density at a given orbital period and the eccentricities of the remaining planetesimals. This trend is largely set by the initial conditions, as the gravitational stirring is more vigorous when bodies are packed together closely and higher eccentricities are required to produce an equilibrating aerodynamic drag force (see equations \ref{eq:vs_timescale} and \ref{eq:ts_stokes}). Despite having significantly different masses, the planetary embryos formed in each case have remarkably similar eccentricities. This is likely due to the fact that inelastic collisions play a more significant role where the solid surface density is highest, which offsets the fact that the initial bodies started off in a dynamically hotter state.

In figure \ref{fig:surfden_iso}, we compare the masses of the resulting protoplanets and planetesimals in all four simulations to each other. Here, the masses are scaled by the isolation mass at the given orbital distance (see equation \ref{eq:iso}). In all four cases, the masses follow a similar trend: interior to about 60 days in orbital period, protoplanets grow to a factor of a few larger than $M_{iso}$. Exterior to this point, the protoplanet masses roughly stay near the isolation mass. Despite the drastically different solid surface density profiles used, the masses of the largest bodies in all four cases follow a similar trend with orbital period. This indicates that the highly efficient accretion mode seen at shorter orbital periods is dependent on the sizes of the individual bodies themselves, rather than how they are distributed. The transition visible near 60 days in all cases also supports our conclusion that planetesimal accretion is largely complete everywhere in the disk.
% fdLo needs to run a bit longer

@@

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{figures/smooth_frac.png}
    \caption{Caption goes here.\label{fig:smooth_frac}}
\end{center}
\end{figure}

Show planetesimal distribution for each embryo, will look at this in more detail in paper 2

Show smooth vs chunky accretion plot for each embryo. Boundary visible at 60d
